%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% Friggeri Resume/CV
% XeLaTeX Template
% Version 1.0 (5/5/13)
%
% This template has been downloaded from:
% http://www.LaTeXTemplates.com
%
% Original author:
% Adrien Friggeri (adrien@friggeri.net)
% https://github.com/afriggeri/CV
%
% License:
% CC BY-NC-SA 3.0 (http://creativecommons.org/licenses/by-nc-sa/3.0/)
%
% Important notes:
% This template needs to be compiled with XeLaTeX and the bibliography, if used,
% needs to be compiled with biber rather than bibtex.
%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\documentclass[]{friggeri-cv} % Add 'print' as an option into the square bracket to remove colors from this template for printing

\addbibresource{bibliography.bib} % Specify the bibliography file to include publications

\begin{document}

\header{mathieu}{gaborit}{} % Your name and current job title/field

%----------------------------------------------------------------------------------------
%	SIDEBAR SECTION
%----------------------------------------------------------------------------------------

\begin{aside} % In the aside, each new line forces a line break
\section{contact}
Appartement 4
Domaine les Happelières
Trangé, 72650 Sarthe
France
~
+33(0) 687 59 49 09
~
\href{mailto:mathieu@matael.org}{mathieu@matael.org}
\href{http://blog.matael.org}{blog.matael.org}
\href{http://twitter.com/matael}{@matael}
\section{languages}
French native locutor
English fluency
Spanish basics
Lojban concept
\section{programming}
{\color{red} $\varheartsuit$} Python
~
C, PHP, Perl, Octave/MATLab, CSS3 \& HTML5 -- comfortable
~
Scala, Ruby, Bash, Javascript -- basics
\section{objectives}
As a student in mechanics and acoustics, I would accept any job in that field featuring research and eventually
teaching.
~
I would be glad to work in the field of industry as long as lab work is part of my job.
\end{aside}


%----------------------------------------------------------------------------------------
%	EDUCATION SECTION
%----------------------------------------------------------------------------------------

\section{education}

\begin{entrylist}
%------------------------------------------------
\entry
{2011--2013}
{{\normalfont Candidate for a License SPI.} Bachelor of Science {\normalfont equivalent}}
{Université du Maine, Le Mans, France}
{Specialisation in Acoustics \\\emph{Main Topics}: Acoustics, Waves and Propagation
modelisation, Kinetics, General Physics, Materials Resiliency}
%------------------------------------------------
\entry
{2008--2011}
{{\normalfont Baccalauréat Scientifique} A Level} 
{Lycée St Joseph, La Roche sur Yon, France}
{\emph{Cursus:} Engineering Sciences, Maths specialisation, Music, Latin}
%------------------------------------------------
\end{entrylist}

%----------------------------------------------------------------------------------------
%	WORK EXPERIENCE SECTION
%----------------------------------------------------------------------------------------

\section{experience}

\begin{entrylist}
%------------------------------------------------
\entry
{2012--Now}
{HAUM (organisation)}
{Le Mans, France}
{\emph{Co-Founder \& President} \\
HAUM (Hackerspace de l'Université du Maine) is a structure that promotes
understanding and modification of systems by experimentation.
Role :
\begin{itemize}
    \item Association creation and promotion
    \item Organisation of several events
    \item Working with city structures and services for projects
\end{itemize}
}
%------------------------------------------------
\entry
{2013}
{La Ruche Numérique}
{Le Mans, France}
{\emph{Associate Speaker}\\
Topics :
\begin{itemize}
    \item Coworking and Online tools (fr)
    \item OpenData (fr)
\end{itemize}}
%------------------------------------------------
\entry
{2010-2013}
{Bar-Jazz Les Alizés}
{Saint Gilles Croix de Vie, Vendée, France}
{\emph{Waiter}}
%------------------------------------------------
\end{entrylist}

%----------------------------------------------------------------------------------------
%	AWARDS SECTION
%----------------------------------------------------------------------------------------

\section{projects}

\begin{entrylist}
%------------------------------------------------
\entry
{2013}
{Haumelitta}
{HAUM}
{Twitter-enabling for a coffee pot. It's now capable of receiving orders from the Twitter social network.}

\entry
{2013}
{pyTimeo and TimeoAPI}
{HAUM}
{Providing an easy-to-access-and-use API for TIMEO service (from Le Mans transportation network operator).
Code and concept is free-software and under open licenses.}

\entry
{2012}
{Auralization : Comparison of different factors on the auralization process}
{université du Maine, Le Mans, France}
{Intending to compare effects of different measurement factors on the auralization process.}
%------------------------------------------------
\end{entrylist}

%----------------------------------------------------------------------------------------
%	COMMUNICATION SKILLS SECTION
%----------------------------------------------------------------------------------------

\section{miscellaneous}

\begin{entrylist}
%------------------------------------------------
\entry
{Interests}{}{}
{Security in human or computer systems, Opendata, Free Software movement, Juggling}

\entry
{Other skills}{}{}
{Team work, presentation fluency, Tinkerer, Bulimic curious, Make good coffee}

\end{entrylist}

\end{document}
