%-------------------------------------------------------------------------------
%	SECTION TITLE
%-------------------------------------------------------------------------------
\cvsection{Extras}


%-------------------------------------------------------------------------------
%	CONTENT
%-------------------------------------------------------------------------------
\begin{cventries}

%---------------------------------------------------------
  \cventry
    {Co-founder} % Affiliation/role
    {HAUM -- Hackerspace Au Mans} % Organization/group
    {Le Mans, France} % Location
    {Sep. 2011 --} % Date(s)
    {
      \begin{cvitems} % Description(s) of experience/contributions/knowledge
				\item {Setup of the student-oriented hackerspace.}
				\item {Legal creation of the organization in 2012.}
        \item {President from Nov. 2012 to Nov. 2015.}
				\item {Community development, projects, conferences \& several events.}
				\item {Website: \href{https://haum.org}{haum.org}}
      \end{cvitems}
    }

%---------------------------------------------------------
  \cventry
    {Organiser} % Affiliation/role
    {24 Heures du Code} % Organization/group
    {Le Mans, France} % Location
    {2014 -- 2016} % Date(s)
    {
      \begin{cvitems} % Description(s) of experience/contributions/knowledge
        \item {Submitted problems :
					\begin{description}
						\item[2014] A Firefox OS application on transportation open-data (partner: Mozilla Foundation)
						\item[2015] Urban Flow : opendata-based arena for artificial intelligences
						\item[2016] SartheDev API : unsual exploration of open datasets
					\end{description}
				}
				\item {Planning and \textit{in-situ} event management}
      \end{cvitems}
    }

%---------------------------------------------------------
  \cventry
    {Co-founder} % Affiliation/role
    {Sample.Cat} % Organization/group
		{Le Mans, FR --- Sheffield, UK} % Location
    {Dec. 2015 --} % Date(s)
    {
      \begin{cvitems} % Description(s) of experience/contributions/knowledge
				\item {Analysis of social media streams after social crisis.}
				\item {Hybrid Project: statistical analysis, machine learning, sociology}
				\item {Several conferences :\begin{itemize}
						\item HAUMTalks \#3 -- \textit{\#ParisAttacks : A pretext to sentiment analysis on social media (fr)}
						\item PSES-HSF 2016 -- \textit{How Twitter activity shows sentiments of a shocked population?}
				\end{itemize}}
				\item {Innovative techniques to gather, store and analyse large datasets.}
				\item {Website: \href{https://sample.cat}{sample.cat}}
      \end{cvitems}
    }

%---------------------------------------------------------
\end{cventries}
